\textbf{The Illusion Game: A Novel Experimental Paradigm Provides Evidence in Favour of a General Factor of Visual Illusion Sensitivity and Personality Correlates}

### 2022-09-06 manuscript.Rmd
duplcate ref

Using the parametric illusion generation framework we developed, *Pyllusion* [@makowski2021a], we have hence shown that illusions can be manipulated continuously across several different visual illusions. This opens the door for new illusions-based paradigms and tasks, therefore making it possible for future researchers to directly manipulate specific features and parameters of the illusion that are of interest. The validation of this novel framework also affords future illusion scientists a standardized measure of illusion susceptibility, instead of relying on conventional methods that depend upon participants' subjective perceptions. In our paradigm, in which we apply this approach to a reaction-time task, we were able to measure inter-individual scores of objective illusion sensitivity.

>>>>

Using the parametric illusion generation framework developed with *Pyllusion* [@makowski2021], we have hence shown that illusions can be manipulated continuously across several different visual illusions. This opens the door for new illusions-based paradigms and tasks, therefore making it possible for future researchers to directly manipulate specific features and parameters of the illusion that are of interest. The validation of this novel framework also affords future illusion scientists a standardized measure of illusion susceptibility, instead of relying on conventional methods that depend upon participants' subjective perceptions. In our paradigm, in which we apply this approach to a reaction-time task, we were able to measure inter-individual scores of objective illusion sensitivity.
